The human in the loop: volunteer computing as a socio-technical system

### 2016-03-09 PPSN2016/paper.Rnw
Inserted data in paper

\begin{document}
\title{The human in the loop: volunteer computing as a socio-technical
system}

>>>>

\begin{document}

<<setup, cache=FALSE,echo=FALSE>>=
library("ggplot2")
experiment.data <- data.frame(Experiment=character(),
                              milliseconds=character(),                           
                              IPs=character(), 
                              actualIPs=character(),
                              PUTs=character(),
                              actualPUTs=character())

these.experiments <- c("nooverlap-1","nooverlap-newgraph", "nooverlap-newgraph-2","nooverlap-newgraph-3","nooverlap-newgraph-reboot","nooverlap-newgraph-reboot-cachecrash")

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-time-cache-2016-03-cache=32-",i,".csv"))

    experiment.data <- rbind( experiment.data,
                             data.frame( Experiment=rep(i, length(this.data$IPs)),                   
                                        milliseconds=as.integer(this.data$milliseconds),
                                        IPs=as.integer(this.data$IPs),
                                        actualIPs=as.integer(this.data$actualIPs),
                                        PUTs=as.integer(this.data$PUTs),
                                        actualPUTs=as.integer(this.data$actualPUTs)))

}

experiment.data$newgraph <- grepl("newgraph",experiment.data$Experiment)
experiment.data$nooverlap <- grepl("nooverlap",experiment.data$Experiment)
experiment.data$reboot <- grepl("reboot",experiment.data$Experiment)
experiment.data$cachecrash <- grepl("cache",experiment.data$Experiment)

time.data <- data.frame(Experiment=character(),
                        minute=as.Date(character()),
                        IPs=character())

these.experiments <- c("nooverlap-0","nooverlap","nooverlap-newgraph","nooverlap-newgraph-reboot-cachecrash")

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-per-minute-cache=32-",i,".csv"))
    time.data <- rbind(time.data,
                       data.frame(Experiment=rep(i,length(this.data$IPs)),
                                  minute=strptime(this.data$time,"%Y-%m-%d %H:%M"),
                                  IPs=as.integer(this.data$IPs))
                       )
}
@

\title{The human in the loop: volunteer computing as a socio-technical
system}
